---
title: "Using `wbwdi` to access World Development Indicators"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using `wbwdi` to access World Development Indicators}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(wbwdi)
```

The `wbwdi` package provides a modern and flexible interface for accessing the World Bank’s [World Development Indicators (WDI)](https://datatopics.worldbank.org/world-development-indicators/). With `wbwdi`, you can download data for multiple indicators and geographies in a single function call, benefit from progress bars, and receive the output in a tidy data format, making it ideal for further analysis with other data sources.

## Installation

To install the development version of `wbwdi`, use:

```{r eval=FALSE}
pak::pak("tidy-intelligence/r-wbwdi")
```

## Listing supported indicators

The `wbwdi` package allows you to retrieve a full list of all supported indicators from the World Bank [Indicators API](https://datahelpdesk.worldbank.org/knowledgebase/articles/889392-about-the-indicators-api-documentation). Each indicator is accompanied by metadata such as its unit of measurement, source, and associated topics.

```{r}
wdi_get_indicators()
```

You can also get the list of supported indicators in a different language. For example, to retrieve the indicators in Spanish:

```{r}
wdi_get_indicators(language = "es")
```

To get the list of languages supported by the API, call: 

```{r}
wdi_get_languages()
```

Note that not all indicators might be translated into all languages. 

## Listing supported geographies

You can retrieve a list of all geographies supported by the World Bank API along with metadata such as region, administrative region, income level, and lending type.

```{r}
wdi_get_geographies()
```

This information can also be requested in other languages. For example, to view the supported geographies in Chinese:

```{r}
wdi_get_geographies(language = "zh")
```

### Downloading indicator data

With `wbwdi`, you can download indicator data for multiple geographies and indicators in a single function call. The function returns a tidy data frame with country, indicator, date, and value columns.

For example, to download GDP per capita and total population for Mexico, Canada, and the United States:

```{r}
wdi_get(
  geographies = c("MX", "CA", "US"),
  indicators = c("NY.GDP.PCAP.KD", "SP.POP.TOTL")
)
```

If you need the same indicators for all geographies, you can pass `"all"` as the `geographies` parameter:

```{r}
wdi_get(
  geographies = "all",
  indicators = c("NY.GDP.PCAP.KD", "SP.POP.TOTL")
)
```

## Other helper functions

You can fetch a list of all supported regions, sources, topics and lending types, respectively, using the corresponding helper function:

```{r eval=FALSE}
wdi_get_regions()
wdi_get_sources()
wdi_get_topics()
wdi_get_lending_types()
```

If you want to search for specific keywords among indicators or other data sources, you can use the RStudio or Positron data explorer. Alternatively, this package comes with a helper function:

```{r}
indicators <- wdi_get_indicators()
wdi_search(
  indicators,
  keywords = c("inequality", "gender"),
  columns = c("indicator_name")
)
```

## Conclusion

The `wbwdi` package is designed to simplify the process of accessing and analyzing World Bank data and combining it with other data sources. By offering features like multi-indicator downloads, progress bars, and flexible language support, `wbwdi` is a robust tool for users who need access to World Development Indicators in a tidy format.

If you encounter any errors or have suggestions for improvements, please consider opening an issue in the package repository on [GitHub](https://github.com/tidy-intelligence/r-wbwdi/issues).
